---
title: A fake dashboard
---

```{r}
#| include: false

library(tidyverse)
library(scales)
library(pins)

board <- board_folder("../pins")
```

# Presidential details

```{r}
#| include: false

pres_results <- board |> pin_read("results_presidential")
```

Total votes: `r label_comma()(pres_results)`

# Congressional details

## CD 1
```{r}
#| include: false

cd1_results <- board |> pin_read("results_cd1")
```

Total votes for `r cd1_results$district`: `r label_comma()(cd1_results$total)`

## CD 2

```{r}
#| include: false

cd2_results <- board |> pin_read("results_cd2")
```

Total votes for `r cd2_results$district`: `r label_comma()(cd2_results$total)`


# County details

```{r}
#| include: false

ada <- board |> pin_read("ada_cleaned")
bannock <- board |> pin_read("bannock_cleaned")
bonneville <- board |> pin_read("bonneville_cleaned")
canyon <- board |> pin_read("canyon_cleaned")
kootenai <- board |> pin_read("kootenai_cleaned")
madison <- board |> pin_read("madison_cleaned")
twin_falls <- board |> pin_read("twin_falls_cleaned")
```


## `r ada$county`

Last updated: `r format(ymd_hms(ada$timestamp), "%B %d, %Y at %I:%m %p")`

Total votes: `r label_comma()(ada$vote_total)`


## `r bannock$county`

Last updated: `r format(ymd_hms(bannock$timestamp), "%B %d, %Y at %I:%m %p")`

Total votes: `r label_comma()(bannock$vote_total)`


## `r bonneville$county`

Last updated: `r format(ymd_hms(bonneville$timestamp), "%B %d, %Y at %I:%m %p")`

Total votes: `r label_comma()(bonneville$vote_total)`


## `r canyon$county`

Last updated: `r format(ymd_hms(canyon$timestamp), "%B %d, %Y at %I:%m %p")`

Total votes: `r label_comma()(canyon$vote_total)`


## `r kootenai$county`

Last updated: `r format(ymd_hms(kootenai$timestamp), "%B %d, %Y at %I:%m %p")`

Total votes: `r label_comma()(kootenai$vote_total)`


## `r madison$county`

Last updated: `r format(ymd_hms(madison$timestamp), "%B %d, %Y at %I:%m %p")`

Total votes: `r label_comma()(madison$vote_total)`


## `r twin_falls$county`

Last updated: `r format(ymd_hms(twin_falls$timestamp), "%B %d, %Y at %I:%m %p")`

Total votes: `r label_comma()(twin_falls$vote_total)`
